European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-11 manuscript/manuscript.qmd
Switch to Chi-squared test for Probit (#26)
* bugfix: probit model name

* switch to Chisq test for probit in code

* store new object

* Update footnote

[^12]: Based on an $F$-test for the null hypothesis that USA=EUP. The associated $p$-values are 0.021 and 0.014, respectively. For loan approval, the difference is nearly significant at the 10% level ($p=0.122$).

>>>>

[^12]: Based on tests of equality for the null hypothesis that $\text{USA} = \text{EUP}$. $F$-tests are used for the linear models; for the Probit model, the test corresponds to an asymptotic Chi-squared statistic, which is appropriate given the large sample size ($N = 522$). The $p$-values for the first two models are 0.021 and 0.014, respectively. For loan approval, the difference is nearly significant at the 10% level ($p = 0.122$).
